\LARGE \bf When Children Teach a Robot to Write: An Autonomous Teachable Humanoid Which Uses Simulated Handwriting

### 2014-12-12 rebuttal_sorted.txt

>    - vague writing -
>
>    “provides context for robotics in education” - What is meant by
>    context here?
DONE

>
>    “which is capable of generating the necessary letter models” -
>    Necessary according to what criteria?
DONE

All points have been well taken and the feedback will be incorporated to improve readability.

>    Also, I recommend removing “Those who cannot do, teach” from the
>    title. This phrase is an insult to teachers, and it’s unclear how
>    it’s relevant to this work.
DONE
The title was meant to re-purpose the idiom in the context of children with handwriting difficulties having an opportunity to improve through teaching. We appreciate this reviewer bringing to light the potential for this to strike a nerve with teachers and will accept their recommendation.

### 2014-12-12 main.tex
update title
R1 scaffolding conclusion comment

\title{\LARGE \bf
Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting %still not sure
% what about:
% When Children Teach a Robot to Write
% ?
}

@@

We believe that this article introduces three noteworthy contributions: an innovative
application of data processing and artificial intelligence for the
learning of hand-written letters suitable for educative purposes; a robotic
system which has been experimentally shown to provide convincing scaffolding for
complex human-robot interactions (teacher-learner social interactions, learning by
demonstration, simulated robotic fine motor skills); and an initial experimental investigation of what appears to be a
new role for robots in education.

Specifically, the technical challenges involved in developing a teachable
robotic agent in the context of handwriting which have been addressed in this
work include:

    \item developing capabilities for a robot with limited fine motor
        capabilities, in particular the {\sc nao} robot, to engage in the act of handwriting in a
        way which is believable for interacting with children. This is
        accomplished by leveraging simulated handwriting with a synchronised
        tablet communicating via ROS;

    \item developing an algorithm capable of incorporating user feedback and
        demonstrations in order to adapt artificially generated handwriting quality so as
        to simulate a teachable agent, which has been implemented by maintaining
        a learning algorithm in the parameter space of the PCA-based shape models and
        converging towards the parameters of user demonstrations; and

    \item integrating the system into a working interaction suitable for
        engaging children in the learning by teaching paradigm, accomplished by
        fusing the robotic drawing capabilities and the learning algorithm for
        handwritten letters established with a central controller which manages
        the flow of the interaction, turn taking and integration of the connected 
	devices.

>>>>

\title{\LARGE \bf
When Children Teach a Robot to Write: An Autonomous Teachable Humanoid Which Uses Simulated Handwriting
}

@@

We believe that this article introduces three noteworthy contributions: an 
innovative application of artificial intelligence for the learning of 
hand-written letters suitable for educative purposes; a method for a 
commercially affordable humanoid, in particular the {\sc nao} robot, to exhibit
simulated fine motor capabilities; and a working autonomous interaction 
suitable for engaging children in complex human-robot interactions, such as 
teacher-learner social interactions and learning from demonstration.
